---
title: "gender_analysis"
---
Load required packages.

```{r setup, include=FALSE}
require("gender")
```


Set up workspace, i.e., remove all existing data from working memory, initialize the random number generator, turn of scientific notation of large numbers, set a standard theme for plotting, etc.

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rm(list=ls())
set.seed(42)
options(scipen=10000)
```


Load data from CSV file.

```{r}
airbnb_df <- read.csv("airbnb_clean.csv", header=TRUE)
```


#MULTIPLE HOSTINGS 


```{r}

results <- airbnb_df %>%
  group_by(host_id) %>%
  count(host_name) %>%
  ungroup() %>%
  arrange(desc(n)) 



top_hosts <- unique(airbnb_df[airbnb_df$calculated_host_listings_count > 50, c("host_name", "host_id", "calculated_host_listings_count")])

p <- top_hosts %>%
  ggplot(mapping = aes(x = host_name, y = calculated_host_listings_count)) +
  geom_bar(stat = "identity") +
  labs(title = "Top Hosts with Calculated Listings Count > 50", x = "Host Name", y = "Calculated Listings Count") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))

quantile(airbnb_df$calculated_host_listings_count, 0.95)


```

Only 5% of listings have more than 15 listings. With this, 15 listings seem as reasonable a threshold as any to distinguish between hosts who rent on Airbnb professionally and those who do not. We've binned them into two groups (professional/casual) and compared the price (log), number of reviews (log), reviews per month (log) using box plots.

```{r}
airbnb_df <- airbnb_df %>% 
  mutate(host_category = cut(calculated_host_listings_count, 
                        breaks = c(0, 15, max(calculated_host_listings_count)),
                        labels = c("professional", "casual"),
                        include.lowest = TRUE)) %>% mutate(host_category = as.factor(host_category))


p <- ggplot(airbnb_df, aes(x = host_category, y = log_price)) +
  geom_boxplot() +
  labs(
    title = "Price by Host Group",
    x = "Host Group",
    y = "Price"
  )

ggsave("boxplot_host_category_log_price.png", plot = p, width = 6, height = 4, dpi = 300)

ggplot(airbnb_df, aes(x = host_category, y = log_reviews_per_month)) +
  geom_boxplot() +
  labs(
    title = "Reviews per month by Host Group",
    x = "Host Group",
    y = "Revies per Month"
  )

ggplot(airbnb_df, aes(x = host_category, y = log_number_of_reviews)) +
  geom_boxplot() +
  labs(
    title = "Number of Reviews by Host Group",
    x = "Host Group",
    y = "Number of Reviews"
  )

ggplot(airbnb_df, aes(x = host_category, y = log(lowest_monthly_earnings))) +
  geom_boxplot() +
  labs(
    title = "Lowest monthly earnings by Host Group",
    x = "Host Group",
    y = "Lowest monthly earnings"
  )

```

#KIND OF STAY

```{r}
airbnb_df <- airbnb_df %>% 
  mutate(category_of_stay = cut(minimum_nights, 
                        breaks = c(0, 28, max(minimum_nights)),
                        labels = c("long-term", "short-term"),
                        include.lowest = TRUE)) %>% mutate(category_of_stay = as.factor(category_of_stay))

ggplot(airbnb_df, aes(x = category_of_stay, y = log(lowest_monthly_earnings))) +
  geom_boxplot() +
  labs(
    title = "Lowest monthly earnings by stay category",
    x = "Category of stay",
    y = "Lowest monthly earnings"
  )

ggplot(airbnb_df, aes(x = category_of_stay, y = log_price)) +
  geom_boxplot() +
  labs(
    title = "Price by stay category",
    x = "Category of stay",
    y = "Price"
  )

```


#MULTIPLE HOSTS

By looking at the data, it seems that sometimes multiple hosts are behind one host_id. There are various ways to identify them. We assume that there is more than one host, if one of the following appears in a host name: "+" , "/", " and ", "&". To make sure we do not include names like "Andrea",  we search for " and " with leading and trailing spaces.

```{r}
# Adds logical column that indicates whether name contains " and ", "+", "/" or "&" ; ignore.case makes sure that all variations of " and " are covered
airbnb_df$is_more_than_one_host <- grepl(" and |&|\\+|/", airbnb_df$host_name, ignore.case = TRUE)
# Adds column that contains vector of all names if is_more_than_one_host is true (more than one host)
airbnb_df$host_names_all <- ifelse(airbnb_df$is_more_than_one_host == TRUE, strsplit(airbnb_df$host_name, "(?i) and |&| & |\\+| \\+ |/| / ", perl=TRUE), c(""))
# Count rows where this is the case
nrow(airbnb_df[airbnb_df$host_names_all != '', ])
```


At least 1852 listings appear to have more than one host. This does not necessarily mean that the rest have only a single host. Considering that companies also list their accommodations on Airbnb, this probably rather represents the minimum. The presence of hosts associated with companies is not part of this analysis and needs further investigations. 

Short look at how many distinct hosts this is: 

```{r}
airbnb_df %>% filter(is_more_than_one_host == TRUE) %>% summarise(count = n_distinct(host_id))
```
There are 1229 distinct host_ids.

#GENDER ANALYSIS

Given the availability of host names, it might be insightful to look at the gender of the hosts and how the gender relates to other variables. 
We will use the gender package (https://github.com/lmullen/gender) to assign a gender classification to each host name. 
The package uses data from the Social Security Administration, the U.S. Census Bureau (via IPUMS USA), and the North Atlantic Population Project. 
We are aware that this approach and therefore the results from this whole section can only be of limited significance and should only be taken as indicator that this might be something worth investigating.

Before we do this, we need to split the values in the column that contains all names and create a row for each name:  

```{r}
#add a new column called "x", filter for all values in "host_names_all" where the list contains more than one value (meaning more than one host) and use unnest to make a separate row for each name in "host_names_all" then rename "host_names_all" to "host_names_splitted" and call "x" "host_name_all" instead
airbnb_df <- airbnb_df %>% mutate(x = host_names_all) %>% filter(lengths(host_names_all) > 0) %>% 
  unnest(host_names_all) %>% rename(host_names_splitted = host_names_all) %>% rename(host_names_all = x)
#add names where empty to splitted column so the original is untouched
airbnb_df$host_names_splitted[!airbnb_df$is_more_than_one_host] <- airbnb_df$host_name[!airbnb_df$is_more_than_one_host]
#ensure airbnb_df stays a data drame
airbnb_df <- as.data.frame(airbnb_df)
```


Now we can assign the sex/gender to each name, using the "gender" package mentioned above. We do this in chunks, to speed up the process. 

```{r}
chunksize <- 100 
#two temporary variables 
min <- 1
max <- 100
#create temporary dataframe
gender <- data.frame()


for(i in 1:ceiling(nrow(airbnb_df)/chunksize)){
  # Check if max is higher than the number of rows in the dataframe to make sure slicing in next line works correctly
  max <- ifelse(max>nrow(airbnb_df), nrow(airbnb_df), max)
  # Select next 100 rows
  row_slice_100 <- airbnb_df[min:max,]
  # Use gender function to assign gender
  host_names_100_gender <- gender(row_slice_100$host_names_splitted, year=2010, method="ssa")
  # Rename the name column that was automatically created by the function gender to make sure it can be joined in the next line and remove duplicate columns
  host_names_100_gender <- host_names_100_gender %>% rename(host_names_splitted = name) %>% distinct(host_names_splitted, .keep_all = TRUE)
  # Join the results from the use of the gender function with the slice of the data frame and drop columns that were automatically added by the function "gender" 
  host_names_gender <- row_slice_100 %>% left_join(host_names_100_gender, by = "host_names_splitted") %>%  dplyr::select(-c(proportion_male, proportion_female, year_min, year_max))
  
  # Add 100 to min and max to select next 100 rows in next iteration
  min <- min+100
  max <- max+100
  #add rows to temporary df gender
  gender <- rbind(gender, host_names_gender)
}
# Assign gender to airbnb_df and make sure it is a data frame
airbnb_df <- as.data.frame(gender)

# Remove all temporary used variables and the temporary data frame
rm(gender, min, max, chunksize, i, row_slice_100, host_names_100_gender, host_names_gender)

airbnb_df$gender <- as.factor(airbnb_df$gender)
```

Let's see if there are hosts with even more than two names by counting all the names associated with a listing id:

```{r}
airbnb_df <- airbnb_df %>%
  group_by(id) %>%
  mutate(host_count = n()) %>%
  as.data.frame()

max(airbnb_df$host_count)

```

There seems to be a few listings with more than even two hosts. Looking at the data there is one with 4 hosts and one with 3. 


We now take a closer look at the "combined" hosts. We only want to assign one gender per host_id, so that we have the same number of rows as in the original dataset. This means we want to categorize into three categories: male, female, mixed.

```{r}
# Create temporary data frame and filter for rows where there is more than one host and then group by host_id and check if gender values are the same and assign the right value
result_df <- airbnb_df %>%
  filter(is_more_than_one_host == TRUE) %>%
  group_by(host_id) %>%
  summarise(result = if (length(unique(gender)) == 1) unique(gender) else "mixed")

# Merge the result back into the original data frame
airbnb_df <- left_join(airbnb_df, result_df, by = "host_id")
airbnb_df <- airbnb_df %>%
  mutate(gender = case_when(
    !is.na(result) ~ result,
    TRUE ~ gender  # Keep the original value when the condition is not met
  )) %>% dplyr::select(-c(host_names_splitted, result)) %>% distinct(.keep_all =  TRUE)

rm(result_df)
```


We will now take a look at the gender distribution of the listings in our dataset. Note that hosts can appear more than once. 
LISTINGS VS HOSTS
```{r}
# Counts by gender
gender_counts <- airbnb_df %>%
  group_by(gender) %>%
  summarize(count = n())

# Sum of all entries
total_count <- sum(gender_counts$count)

# Creates a pie chart
ggplot(gender_counts, aes(x = "", y = count, fill = gender)) +
  geom_bar(stat = "identity") +
  coord_polar("y") +
  labs(title = "Gender Distribution") +
  theme_void() + 
  geom_text(aes(label = paste0(gender, "\n", count, " (", scales::percent(count / total_count), ")")), 
            position = position_stack(vjust = 0.5))

# Remove help variables and dfs 
rm(gender_counts, total_count)
```
We can see a slight overrepresentation of female names, but with 20% of the names remaining unidentified this has only limited significance.Next, we will investigate these unidentified names.
Another interesting insight is that most hosts that are more than one person seem to be mixed. Remember 1852 from above and now we see 1516 hosts of mixed gender. 

---------- Bis hier ist alles ready ------------

