---
title: "optimized_price_sin_inf"
output: html_document
date: "2023-10-14"
---

# General Preparation

load packages

```{r load packages}

library(tidyverse)
library(scales)
library(gridExtra)
library(stargazer)

```

setup workspace: clear memory, load data (already cleaned, see data_cleaning.rmd)

```{r setup}

rm(list = ls())
airbnb_df <- read_csv("airbnb_clean.csv")

```


# Feature Engineering

Create variable indicating listings average monthly earnings

Note that we assume that every visitor leaves a review as a reputation system
incentivizes users to do so. Note also, that we are only able to calculate
the lowest potential earnings as we have only insight into the minimum number
of nights visitors need to stay.

```{r}

airbnb_df <- airbnb_df %>%
  mutate(lowest_monthly_earnings = minimum_nights*reviews_per_month*price)

```

# Data Exploration

Examine summary statistics including range, and overview distribution of earnings

```{r}

summary(airbnb_df$lowest_monthly_earnings)

max(airbnb_df$lowest_monthly_earnings) - min(airbnb_df$lowest_monthly_earnings)

airbnb_df %>%
  ggplot(aes(lowest_monthly_earnings)) +
  geom_histogram() +
  scale_y_continuous()

```

As the distribution is extremely skewed to the right, we will conduct a log-transformation

```{r}

# log-transform earnings + filter out infinite values
airbnb_df <- airbnb_df %>%
  mutate(log_earnings = log(lowest_monthly_earnings)) %>%
  filter(is.finite(log_earnings), is.finite(log_price), is.finite(log_reviews_per_month))

# store summary statistics of earnings distribution
# upper whisker
IQR <- IQR(airbnb_df$log_earnings)
calc_upper_whisker <- (quantile(airbnb_df$log_earnings, probs = 0.75) + IQR*1.5)
select_upper_whisker <- airbnb_df$log_earnings >= calc_upper_whisker
upper_whisker <- airbnb_df$log_earnings[select_upper_whisker]
upper_whisker <- min(upper_whisker)

# lower whisker
calc_lower_whisker <- (quantile(airbnb_df$log_earnings, probs = 0.25) - IQR*1.5)
select_lower_whisker <- airbnb_df$log_earnings <= calc_lower_whisker
lower_whisker <- airbnb_df$log_earnings[select_lower_whisker]
lower_whisker <- max(lower_whisker)

# upper and lower quartile and median
earnings_distribution <- c(
                           min(airbnb_df$log_earnings), 
                           quantile(airbnb_df$log_earnings, probs = c(0.25, 0.5, 0.75)),
                           max(airbnb_df$log_earnings))

#draw histogram
airbnb_df %>%
  ggplot(aes(x = log_earnings)) +
  geom_histogram() +
  labs(title="Earnings Distribution") +
  xlab("Logged Earnings") +
  ylab("Frequency") 

# draw boxplot showing delogged values
airbnb_df %>%
  ggplot(aes(y = log_earnings)) +
  geom_boxplot() +
  stat_boxplot(geom = "errorbar") +
  scale_y_continuous(breaks = c(earnings_distribution, lower_whisker, upper_whisker), 
                     labels = as.integer(exp((c(earnings_distribution, lower_whisker, upper_whisker))))) +
  scale_x_continuous(breaks = NULL, labels = NULL) +
  labs(
    y = "Lowerst Monthly Earnings (De-Logged)",
    title = "Earnings Distribution"
  )

# violin plot by neighbourhood groups
airbnb_df %>%
  ggplot(aes(x = reorder(neighbourhood_group, +lowest_monthly_earnings), y = log_earnings)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = TRUE) +
  labs(
    title = "Earnings Distribution by Earnings",
    x = ""
  )


```

The lowest monthly earnings are approximately normally distributed.
50% of listings have earned up to 225 per month. 75% of listings have earned up to 612 per month.
There is much more variance in monthly earnings in the upper 25% of the distribution.
As seen in the original boxplot, some outliers have extremely high earnings.


```{r}
# create vector inidicating position in earnings distribution
q9 <- quantile(airbnb_df$lowest_monthly_earnings, probs = 0.9)
quantile_indicator <- ifelse(airbnb_df$lowest_monthly_earnings > q9, "upper 10%", "lower 90%")
airbnb_df <- cbind(airbnb_df, quantile_indicator)

# 
earningsplot_df <- airbnb_df %>%
  group_by(quantile_indicator) %>%
  summarize(
    tot_earnings_mio = (sum(lowest_monthly_earnings)/1000000)
  )

earningsplot_df %>%
  ggplot(aes(quantile_indicator, tot_earnings_mio)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.2f", earningsplot_df$tot_earnings_mio)), vjust = -0.5, size = 3) +
  scale_y_continuous(breaks = seq(0, max(earningsplot_df$tot_earnings_mio), by = 3)) +
  labs(
    title = "Total Earnings of upper 10% and lower 90% of Distribution",
    y = "Lowest Monthley Earnings in Mio",
    x = NULL
  )
ggsave("tot_earn_by_distribution.pdf")

```

The upper 10% of listings earn almost 150% of the lower 90%.

```{r}
# examine how much each neighbourhood group earns and the share of room types for each

earningsplot_hood_room <- airbnb_df %>%
  group_by(neighbourhood_group, room_type) %>%
  summarize(
    tot_earnings_mio = (sum(lowest_monthly_earnings)/1000000),
  )

n_hood <- airbnb_df %>%
  group_by(neighbourhood_group) %>%
  summarise(
    count = n())

earningsplot_hood_room %>%
  ggplot(aes(x = reorder(neighbourhood_group, +tot_earnings_mio), y = tot_earnings_mio, fill = room_type)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks = seq(0, 20, by = 1)) +
  labs(
    title = "Total Earnings by Neighbourhood and Room Type",
    y = "Lowest Monthly Earnings in Mio",
    x = NULL,
    fill = "Room Type"
  )

```
Home-type listings in Manhattan generate the most earnings

```{r}

# Relationships between earnings and other variables

airbnb_df %>%
  ggplot(aes(x = , y = log_earnings))
```



  

